GPU Acceleration of Edge-Based Motion Detection and Machine Learning-Aided Facial Recognition with NVIDIA CUDA

### 2015-12-16 documents/paper/paper.tex
Add Python listing for facial recognition

\subsection{High-Level Python Implementation}
The Python OpenCV library exposes an API for the entire Canny edge detection algorithm. The Canny algorithm is similar to, but more nuanced than, our algorithm, substituting our selective thresholding procedure for hysteresis. However, the end results are very similar. As is evident from Listing \ref{python-edge-detection-implementation}, the procedure is very straightforward.
\begin{lstlisting}[
	caption=Python implementation of Canny edge detection with OpenCV,
	label=python-edge-detection-implementation,
	language=Python
]
LOW_THRESHOLD = 100
HIGH_THRESHOLD = 200
edges = cv2.Canny(img, LOW_THRESHOLD, HIGH_THRESHOLD)
\end{lstlisting}

@@

>>>>

\subsection{High-Level Python Implementation}
The Python OpenCV library exposes an API for the entire Canny edge detection algorithm. The Canny algorithm is similar to, but more nuanced than, our algorithm, substituting our selective thresholding procedure for hysteresis. However, the end results are very similar. As is evident from Listing \ref{python-edge-detection-implementation}, the procedure is very straightforward.
\begin{lstlisting}[
	caption=Python implementation of Canny edge detection with OpenCV,
	label=python-edge-detection-implementation,
	language=Python
]
import cv2

LOW_THRESHOLD = 100
HIGH_THRESHOLD = 200

edges = cv2.Canny(img, LOW_THRESHOLD, HIGH_THRESHOLD)
\end{lstlisting}

@@

\subsection{High-Level Python Implementation}
We again provide sample Python code to demonstrate how the facial recognition algorithm would be implemented on a high level, with the details of implementation abstracted out. The Python OpenCV library exposes an API for facial recognition via a cascade classifier, as shown in Listing \ref{python-facial-recognition-implementation}.
\begin{lstlisting}[
	caption=Python implementation of facial recognition with OpenCV,
	label=python-facial-recognition-implementation,
	language=Python
]
import cv2

IMAGE = 'richb.jpg'
CASCADE_DATA = 'haarcascade_frontalface_default.xml'

face_cascade = cv2.CascadeClassifier(CASCADE_DATA)
faces = face_cascade.detectMultiScale(
	cv2.imread(IMAGE, cv2.IMREAD_GRAYSCALE),
	scaleFactor=1.1,
	minNeighbors=5,
	minSize=(30, 30),
	flags=cv2.CASCADE_SCALE_IMAGE,
)
# faces now contains tuples indicating the location and size of each detected face in the image
\end{lstlisting}
